Opening up the court (surface) in tennis grand slams

### 2019-02-26 contest/surface-type/paper-tennis.Rmd
added correlation matrix figure

## To change into library(courtsports)
library(courtsports)

@@

>>>>

## To change into library(courtsports)
devtools::load_all("~/courtsports")

@@

wim_inds <- which(gs$tournament == "Wimbledon")
head(gs[wim_inds,])

serena_inds <- which(gs_partial_players$name == "Serena Williams")
gs_partial_players[serena_inds[1],]

head(gs_partial)
djoker_inds <- which(gs_partial_players$name == "Novak Djokovic")
gs_partial_players[djoker_inds[1],]
